Benchmarking Python Deep Learning Frameworks\\ on Language Modeling

### 2016-12-13 paper/main.tex
more paper things

\begin{abstract}
Abstraaaact
\end{abstract}

@@

\subsection{Implementation \& Hyperparameters}
Table~\ref{tab:hyperparams} summarizes the hyperparameters chosen for the experiments; there was no cross-validation done since the evaluative performance of the model trained is irrelevant.
\begin{table}\begin{center}
\begin{tabular}{cc}
\textbf{hyperparam} & \textbf{value} \\\hline
RNN type & \texttt{LSTM} \\
hidden size & $256$ \\
optimizer & \texttt{AdamOptimizer} \\
learning rate & $0.003$ \\
batch size & 25 \\
\end{tabular}
\caption{\label{tab:hyperparams}Hyperparameters used in the experiments}
\end{center}\end{table}

@@

We profile which methods take the most amount of time, and look into a variety of metrics.
\begin{itemize}
\item \verb!achieved_occupancy! - fraction of GPU warps used v.s. total number of warps
\item \verb!sm_efficiency! - how much of the runtime is spent performing actual computation
\item \verb!warp_execution_efficiency! - how efficient is execution within a warp; number of registers per thread is a limiting factor.
\item \verb!warp_nonpred_execution_efficiency! - how efficient is execution within a warp on non-predicated (i.e. non-branching) instructions.
\item \verb!dram_read_throughput! - read throughput
\item \verb!dram_write_throughput! - write throughput
\end{itemize}
\section{Discussion}
When looking to use neural network benchmarks, researchers might want to consider various aspects.
\subsection{Programmer Experience}
When adopting new software frameworks, it is important to consider the potential learning curve, as well as higher-level advantages of each framework.

\subsection{TensorFlow}
Pros: easy to use; good support for RNNs and language models; 
Cons: symbolic computation graph is hard to debug; seems slower than others; 
\section{Conclusion}
\section*{Acknowledgments}
We want to thank Emily Furst for helping us with GPU profiling, specifically understanding the CUDA Profiler documentation.
\newpage
\bibliography{references}
\bibliographystyle{emnlp16}
\end{document}

>>>>

\begin{abstract}
Neural networks are omnipresent in natural language processing. 
We benchmark three popular Python frameworks (DyNet, TensorFlow and Theano) on a realistic NLP task: language modeling.
We find that ...
\end{abstract}

@@

\subsection{Implementation \& Hyperparameters}
In our experiments, we optimized for a standard language modeling objective: \textit{cross-entropy}.

Table~\ref{tab:hyperparams} summarizes the hyperparameters chosen for the experiments; there was no cross-validation done since the evaluative performance of the model trained is irrelevant.
\begin{table}\begin{center}
\begin{tabular}{cc}
\textbf{hyperparam} & \textbf{value} \\\hline
RNN type & \texttt{LSTM} \\
hidden size & $256$ \\
optimizer & \texttt{AdamOptimizer} \\
learning rate & $0.003$ \\
batch size & 25 \\
\end{tabular}
\caption{\label{tab:hyperparams}Hyperparameters used in the experiments}
\end{center}\end{table}

@@

We profile which methods take the most amount of time, and look into a variety of metrics.
\begin{itemize}
\item \verb!achieved_occupancy! - fraction of GPU warps used v.s. total number of warps
\item \verb!sm_efficiency! - how much of the runtime is spent performing actual computation
\item \verb!warp_execution_efficiency! - how efficient is execution within a warp; number of registers per thread is a limiting factor.
\item \verb!warp_nonpred_execution_efficiency! - how efficient is execution within a warp on non-predicated (i.e. non-branching) instructions.
\item \verb!dram_read_throughput! - read throughput
\item \verb!dram_write_throughput! - write throughput
\end{itemize}
\section{Discussion}
When looking to use neural network benchmarks, researchers might want to consider various aspects.
\subsection{Programmer Experience}
When adopting new software frameworks, it is important to consider the potential learning curve, as well as higher-level advantages of each framework.
\subsubsection{DyNet}

\subsubsection{TensorFlow}
Pros: easy to use; good support for RNNs and language models; 
Cons: symbolic computation graph is hard to debug; seems slower than others.
\subsubsection{Theano}
\section{Conclusion}

\section*{Acknowledgments}
We want to thank Emily Furst for helping us with GPU profiling, specifically understanding the CUDA Profiler documentation.
\newpage
\bibliography{references}
\bibliographystyle{emnlp16}
\end{document}
